RDF Constraints Classification Ensuring \\ High Quality of Metadata and Data

### 2015-04-20 paper/paper7/paper7.tex
arxiv articles cited

We recently published a technical report\footnote{\textcolor{red}{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as first appendix of this paper) in which we describe 212 constraints (classified as 53 constraint types) to validate rectangular data (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}), and therefore apply the proposed classification system to several vocabularies to represent both data and metadata \cite{BoschZapilkoWackerowEckert2015}.
In this section, we describe constraints, which are important to ensure \emph{SBE} (meta)data quality, 
associate them with default severity levels, and assign them to $\mathcal{CT}_{C}$ and $\mathcal{CT}_{T}$ constraint types.

@@

We recently published a technical report\footnote{\label{technical-report-2}\textcolor{red}{Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as second appendix of this paper) 
in which we describe the comprehensive evaluation in detail \cite{BoschZapilkoWackerowEckert2015-2}. 
As we evaluated nearly 10 thousand \emph{QB} data sets, we published the evaluation results for each data set in form of one document per SPARQL endpoint\footnote{Available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.
Table \ref{tab:evaluation} shows the evaluation results.

@@

\section{Conclusion and Future Work}
\ke{@KAI: Dieses Kapitel muss ich noch an die Änderungen im Paper anpassen!}
In this paper, we showed in form of a complete real world running example how to represent metadata on person-level data (\emph{Disco}), metadata on aggregated data (\emph{QB}), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
We explained why RDF validation is important in this context and how metadata on person-level data, aggregated data, thesauri, and statistical classifications as well as data on both aggregation levels is validated against constraints to ensure high (meta)data quality\footnote{The first appendix of this paper describing each constraint in detail is available at: \textcolor{red}{\url{http://arxiv.org/abs/XXXXX}} \cite{BoschZapilkoWackerowEckert2015}} (\textbf{contribution 2}, section \ref{rdf-validation}). 
We distinguish two validation types:
(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of data models (section \ref{content-driven-validation}).
(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges (section \ref{technology-driven-validation}).
We determined the default \emph{severity level} for each constraint to indicate how serious the violation of the constraint is
and propose an extensible metric to measure the continuum of severity levels.

We implemented a validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages and to ensure correct syntax, semantics, and integrity of diverse vocabularies such as \emph{Disco, QB, PHDD, SKOS, and XKOS} (section \ref{implementation}).
We exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets by means of 212 $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints of the majority of the constraint types.
We validated more than 4.2 billion triples and 15 thousand data sets\footnote{The second appendix of this paper describing the evaluation in detail is available at: \textcolor{red}{\url{http://arxiv.org/abs/XXXXX}} \cite{BoschZapilkoWackerowEckert2015-2}.} (section \ref{evaluation}).

>>>>

We recently published a technical report\footnote{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/1504.04479}} (serving as first appendix of this paper) in which we describe 212 constraints (classified as 53 constraint types) to validate rectangular data (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}), and therefore apply the proposed classification system to several vocabularies to represent both data and metadata \cite{BoschZapilkoWackerowEckert2015}.
In this section, we describe constraints, which are important to ensure \emph{SBE} (meta)data quality, 
associate them with default severity levels, and assign them to $\mathcal{CT}_{C}$ and $\mathcal{CT}_{T}$ constraint types.

@@

We recently published a technical report\footnote{\label{technical-report-2}Available at: \url{http://arxiv.org/abs/1504.04478}} (serving as second appendix of this paper) 
in which we describe the comprehensive evaluation in detail \cite{BoschZapilkoWackerowEckert2015-2}. 
As we evaluated nearly 10 thousand \emph{QB} data sets, we published the evaluation results for each data set in form of one document per SPARQL endpoint\footnote{Available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.
Table \ref{tab:evaluation} shows the evaluation results.

@@

\section{Conclusion and Future Work}
\ke{@KAI: Dieses Kapitel muss ich noch an die Änderungen im Paper anpassen!}
In this paper, we showed in form of a complete real world running example how to represent metadata on person-level data (\emph{Disco}), metadata on aggregated data (\emph{QB}), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
We explained why RDF validation is important in this context and how metadata on person-level data, aggregated data, thesauri, and statistical classifications as well as data on both aggregation levels is validated against constraints to ensure high (meta)data quality\footnote{The first appendix of this paper describing each constraint in detail is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}} (\textbf{contribution 2}, section \ref{rdf-validation}). 
We distinguish two validation types:
(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of data models (section \ref{content-driven-validation}).
(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges (section \ref{technology-driven-validation}).
We determined the default \emph{severity level} for each constraint to indicate how serious the violation of the constraint is
and propose an extensible metric to measure the continuum of severity levels.

We implemented a validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages and to ensure correct syntax, semantics, and integrity of diverse vocabularies such as \emph{Disco, QB, PHDD, SKOS, and XKOS} (section \ref{implementation}).
We exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets by means of 212 $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints of the majority of the constraint types.
We validated more than 4.2 billion triples and 15 thousand data sets\footnote{The second appendix of this paper describing the evaluation in detail is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.} (section \ref{evaluation}).
